Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-12-15 paper/aldebaran.tex
gadigal
space
orbital

By jointly fitting a Keplerian for the planet with a CARMA model for the stellar oscillations, we obtain a precise estimate of both \numax and the planetary orbital parameters. The planetary parameters we obtain are similar to \citet{Hatzes2015}: period $P = 629.0^{+ 1.7}_{-2.1}$~d, eccentricity $e = 0.168^{+ 0.069}_{- 0.071}$; and radial velocity semi-amplitude $K = 127^{+ 15}_{- 14}$~m/s.

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation. TRW acknowledges the support of the Villum Foundation (research grant 10118).
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and NASA's Astrophysics Data System. The \kepler data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts. This work made use of the \textsc{IPython} package \citep{PER-GRA:2007}; SciPy \citep{scipy};  \textsc{matplotlib}, a \textsc{Python} library for publication quality graphics \citep{Hunter:2007}; \textsc{Astropy}, a community-developed core \textsc{Python} package for astronomy \citep{2013A&A...558A..33A}; and \textsc{NumPy} \citep{van2011numpy}. Some of the acknowledgements were compiled using the Astronomy Acknowledgement Generator.

>>>>

By jointly fitting a Keplerian for the planet with a CARMA model for the stellar oscillations, we obtain a precise estimate of both \numax and the planetary orbital parameters. The planetary orbital parameters we obtain are similar to \citet{Hatzes2015}: period $P = 629.0^{+ 1.7}_{-2.1}$~d, eccentricity $e = 0.168^{+ 0.069}_{- 0.071}$; and radial velocity semi-amplitude $K = 127^{+ 15}_{- 14}$~m/s.

@@

BP is grateful for funding from the Breakthrough Prize Foundation. This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.

The authors would like to acknowledge the Gadigal people of the Eora nation on whose ancestral lands the University of Sydney is built.

Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation. TRW acknowledges the support of the Villum Foundation (research grant 10118).
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and NASA's Astrophysics Data System. The \kepler data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts. This work made use of the \textsc{IPython} package \citep{PER-GRA:2007}; SciPy \citep{scipy};  \textsc{matplotlib}, a \textsc{Python} library for publication quality graphics \citep{Hunter:2007}; \textsc{Astropy}, a community-developed core \textsc{Python} package for astronomy \citep{2013A&A...558A..33A}; and \textsc{NumPy} \citep{van2011numpy}. Some of the acknowledgements were compiled using the Astronomy Acknowledgement Generator.
